---
title: "Package Documentation - Preston Roesslet"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{My Package Documentation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753PRESTONROESSLETFALL23)
```

# Introduction
This is a working description of the functions in my package for MATH4753.

## Data - FIREDAM

I have included the FIREDAM dataset in my package. Below is an example showing how you can use this dataset to get the first 6 lines.
```{r}
head(fire)
```

## Function 1 - `myfun()`

This function takes in a quantitative vector, and then returns another vector of the same size where each index has been raised to the power of 2.

```{r}
myfun(1:10)
```

## Function 2 - `ntickets()`

This function calculates the number of tickets to be sold using discrete distribution and normal approximation. In the example below, t takes in the number of seats on the plane to be 400, with a 0.02 probability that the plane will be overbooked, and a 0.95 probability that a given person will show up.

After it runs, it produces a plot of the discrete distribution and the normal approximation, and also returns a list of values containing the most efficient values of how many tickets should be sold for each calculation.

```{r}
ntickets(400, 0.02, 0.95)
```

## Function 2 - `histo()`
This method creates a historgram of sample means. It takes in an input of `n` for the number, and then the number of iterations, `iter`. In the below example, we start with 10 and have 10000 iterations.
```{r}
histo(n=10,iter=10000)
```

## Function 3 - `myboot2()`

This function uses the bootstrap method to generate a historgam of bootsrap sample means.

```{r}
myboot2(x=fire$DAMAGE)
```

## Function 4 - `linearscatter()`

```{r}
spruce.df = spruce
linearscatter(spruce.df, "Height", "BHDiameter", "Breast Height Diameter (cm)", "Height (m)")
```
